Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Put bibliography on a new page
Better introduction to first approach

The first approach uses a Boolean AND operation combined with depth-buffer
masking.  The basic idea is to mask off everything but the area on the screen
with the intersection, rendering the cubes behind it, the intersection itself,
and then the cubes in front of it.  Then the area of the intersection is masked
off and everything else is drawn depth-sorted.

@@

\bibliographystyle{alpha}
\bibliography{paper.bib}

>>>>

The first approach uses a Boolean AND operation combined with depth-buffer
masking.  The basic idea is render the part of the volume directly behind the
intersection, render the intersection itself, and then render the part of the
volume directly in front of the intersection.  Finally the area of the
intersection is masked off and everything else is drawn depth-sorted with
blending enabled.

@@

\newpage
\bibliographystyle{alpha}
\bibliography{paper.bib}
